\section{Position and duties}
The position covered during the internship period was that of software developer.
This included C and C++ on embedded platforms, and C++ and Python on Linux.

The scope and topic of the various projects was not fixed and changed several times over the course of the internship.
In particular, three main subjects can be isolated, and will be discussed individually in the following sections:

\begin{description}
\item [UAVCAN] Introduction on the activities and projects related to drone components supporting the UAVCAN communication standard
\item [Internal autopilot] Design and implementation of autopilot platform for internal research
\item [Light gimbal] Development project for automotive/defense product
\end{description}


\subsection{UAVCAN}
The initial part of the internship consisted in becoming accustomed with the tools and development platform used internally, at that time consisting of NXP series of microcontrollers called LPC11xx and LPC17xx.
This was accomplished with a series of programming tasks, such as interfacing the evaluation board with different sensors and components.

After having acquired the necessary understanding of the development environment, the focus shifted into experimenting with the UAVCAN library in order to evaluate its capabilities and pitfalls, before integrating it into the existing codebase.
UAVCAN is an open-source project based on CANbus aimed at simplifying communication within a drone peripherals.
Once assessed and verified its functionalities, it has been chosen to start working on a line of compliant products.
The first items were the \emph{UAVCAN UAX board}, a device that can control digital servos and other actuators by means of PWM signals, the \emph{UAVCAN MPU Guard}, which automatically chooses the most efficient power source from those connected to its inputs, and the \emph{UAVCAN Debugger}, which would allow users to probe into their UAVCAN networks and perform several actions (configuring nodes, upload firmwares\dots).

Programming these functionalities implied developing a Hardware Abstraction Layer (HAL) around microcontroller peripherals like ADC, DAC, timers, watchdog, and so forth.
This, in turn, required a fairly solid knowledge of the information in the data sheet and user manual of the MCU.
Another important aspect was the integration of the UAVCAN software library, which proved to be a challenging task due to the scarcity of memory resources --- both storage and SRAM --- in some of the devices.

Despite having gotten very close to completion on the \emph{UAVCAN UAX board}, the project has been put on hold due to major hardware design changes which made the firmware incompatible with the newer iteration.


\subsection{Internal autopilot}
At a later point, it has been agreed to develop an autopilot from stretch, in order to gain an insightful view of how estimation algorithms and navigation systems work.

My involvement in this project consisted in assisting the design of both software and hardware.
After having compiled a list of requirements and specifications, a brief research has been conducted in order to choose the relevant hardware components, such as the internal sensors, communication ports, and microcontroller.
Since the latter was required to have much more computational power than those previously mentioned MCUs, an extensive research has been engaged.
A choice was made after evaluating several development platforms and toolchains.

The software development aspects of the autopilot in which I was involved mainly consisted in drawing several diagrams such as Structure diagram, Interaction diagram, and Sequence diagrams, which helped assess the main tasks and split the workload accordingly.
Due to the increased complexity of the project, a \emph{Real-time Operating System} was necessary to control all the different processes within the autopilot.
After testing several solutions (FreeRTOS, NuttX, eCos\dots) the choice fell on ChibiOS, an open-source RTOS which natively supports the chosen MCU.
Along with setting the structure of the software, I was responsible for integrating the UAVCAN protocol into the RTOS.

After becoming positively impressed with the capabilities of ChibiOS, it seemed relevant to employ it in all future software releases and projects.
However, this required porting the peripheral drivers code to the NXP microcontroller series.
The company allocated one week of development for this task, after which the most basic functionalities were fulfilled (PWM, ADC, GPIOs).
Subsequently, the priority of the other software developers went back into the autopilot, and I was assigned to the last project.


\subsection{Light gimbal}
This project, commissioned by an external client, consisted in developing an electronic controller for a self-stabilizing lamp with remote control and tracking capabilities.

The product --- intended for military usage --- consisted in a 7-LED torch mounted on a 2-axis gimbal powered by sensored BLDC motors, and a portable tracker device with a built-in joystick.
The gimbal can be mounted on vehicles, and would keep the light beam steady at the desired position regardless of road bumps and other sources of disturbance.
It can also be paired with a tracker --- adequately attached to a helmet or gun turret --- in order to mimic its heading.

The main tasks for this project in which I was involved were:
\begin{itemize}
\item Selection of required sensors and MCU, with choice fallen for an emph{inertial measurement unit}, used to track heading, and the LPC1549 microcontroller, due to its peripheral capabilities. These devices have been employed on both the gimbal and the tracker.
\item Implementation of a hardware abstraction layers and APIs for the main building blocks of both gimbal and tracker. Such components were: communication protocols, sensors, motors, buttons, LEDs, settings manager, command line interface, PID controller, data filtering and fusion, process managements and debugging interface.
\item Integration of aforementioned software components in order to fulfill customer use cases.
\end{itemize}

The project revealed to be much more challenging than expected due to mechanical issues and changes in requirements.
Major difficulties have been experienced in regards of achieving a proper sensor placement; slight variations in the commutation sequence for the brushless motors would in fact degrade their torque performances.
As a result, the project is still in development, although having reached its final stage.
So far it takes up about 30 thousands lines of code, including contributions from other developers (mainly involved in the radio communication and pairing mechanism).
